### 2022-05-17 manuscript.Rmd
Remove page break after abstract

authornote: |
  \noindent \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}

  \noindent \addORCIDlink{Shreya Kapoor}{0000-0003-2619-8257}

  \noindent \addORCIDlink{Anne-Sophie Kieslinger}{0000-0001-9240-4077}

abstract: |
  Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning and educational achievement [@shepard1971; @hegarty1999; @johnson2005]. On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013]. When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a]. Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months. We robustly found that male infants recognized novel rotated objects more reliably than female infants. These findings indicate that gender differences in mental rotation are already present in the first months of life.

@@

@@

To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported *within* each experiment by the original authors.
Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% Crl [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Fig.\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_perc(hyp_gender$Post.Prob)`.
The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_gender$sigma2_experiment`$, 95% CrI [`r summ_gender$sigma2_experiment.lower`, `r summ_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_gender$sigma2_article`$, 95% CrI [`r summ_gender$sigma2_article.lower`, `r summ_gender$sigma2_article.upper`] at the article level. This means that `r print_perc(summ_gender$icc)` of the total variance can be attributed to differences *between* articles and `r print_perc(1 - summ_gender$icc)` to differences between experiments *within* articles. The results obtained from our Bayesian analyses were reproduced by classical frequentist three-level meta-analysis and meta-regression models (Supplementary Table\ \@ref(tab:tabs2)).

>>>>

@@

# Abstract

Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning and educational achievement [@shepard1971; @hegarty1999; @johnson2005]. On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013]. When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a]. Here we analyzed effect sizes derived from 59 experiments conducted in 1,798 infants aged 3 to 16 months. We robustly found that male infants recognized novel rotated objects more reliably than female infants. These findings indicate that gender differences in mental rotation are already present in the first months of life.

@@

To confirm the gender difference between males and females we set up another Bayesian meta-analysis, this time focusing on the looking-time contrasts between all-male and all-female groups reported *within* each experiment by the original authors.
Our additional analysis revealed a meta-analytic effect size of $g = `r summ_gender$intercept`$, 95% Crl [`r summ_gender$intercept.lower`, `r summ_gender$intercept.upper`] (Supplementary Fig.\ \@ref(fig:figs1)) and a probability of this effect being greater than zero of `r print_perc(hyp_gender$Post.Prob)`.
The heterogeneity of effect sizes was $\sigma_{\text{Experiment}}^2 = `r summ_gender$sigma2_experiment`$, 95% CrI [`r summ_gender$sigma2_experiment.lower`, `r summ_gender$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{Article}}^2 = `r summ_gender$sigma2_article`$, 95% CrI [`r summ_gender$sigma2_article.lower`, `r summ_gender$sigma2_article.upper`] at the article level. This means that `r print_perc(summ_gender$icc)` of the total variance can be attributed to differences *between* articles and `r print_perc(1 - summ_gender$icc)` to differences between experiments *within* articles.

The results obtained from our Bayesian analyses were reproduced by classical frequentist three-level meta-analysis and meta-regression models (Supplementary Table\ \@ref(tab:tabs2)).
